MNRAS \LaTeXe\ template -- title goes here

### 2018-09-19 paper.tex
Adding list of figures

Temporary list of figures:
\begin{enumerate}
\item One
\item Two
\end{enumerate}

>>>>

Temporary list of figures:
\begin{enumerate}
\item Mean Halo Mass vs. Redshift - plotted with Machacek relation - mean\_mass\_errorb\_fix.png
\item Jlw/J21 total vs. Halo Mass colored by redshift - plotted with Machacek relation - jlw\_mass\_machacek\_total.png
\item Percentage of Halos Below Machacek - percent\_below\_dz1.png 
\item Jlw/J21 vs. Halo Mass colored by redshift - plotted with Machacek relation ??  - jlw\_mass\_machacek.png
\item Halo mass vs. redshift colored by total Jlw - plotted with background Machacek relation ?? - mass\_redshift\_machacek\_clocal.png
\item SFRD of PopIII Stars - pop3\_SFR\_bar.png
\item Total # of PopIII Stars vs. Halo mass 2d histogram - tot\#p3\_halomass\_sidehist.png
\item Total mass of PopIII stars vs. halo mass 2d histogram - plotted with SFE - totp3mass\_halomass\_sidehist.png

\end{enumerate}
